A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-03-24 paper/draft.tex
frontline providers

Party members are relatively concentrated in high level bureaucrat positions, such as managers and directors. These are also the best paying positions and the ones with the highest proportion of career protection in the form of contract tenure (\emph{estatutário}). Moving down the hierarchy, it is clear that party members predominantly occupy high level positions, in particular staying at the

>>>>

Party members are relatively concentrated in high level bureaucrat positions, such as managers and directors. These are also the best paying positions and the ones with the highest proportion of career protection in the form of contract tenure (\emph{estatut'{a}rio}). Moving down the hierarchy, it is clear that party members predominantly occupy high level positions, with a much larger prevalence of party members in bureaucrat low, frontline high and then frontline low, as compared to other positions in the bureaucracy.
